Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-05-19 ms.tex
Updates from ShareLaTeX
added a short description of the spot models and some preliminary figures from Theodora.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.4\textwidth]{temperature_drawing.pdf}
\caption{A simple two region model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
\end{centering}
\end{figure}

>>>>

\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{e_1821_096_map.png}\\
\includegraphics[width=0.45\textwidth]{e_1821_120_map.png}
\hspace{0.2in}
\includegraphics[width=0.45\textwidth]{e_1821_126_map.png}
\caption{{\it Aeolus} maps of the light curves at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.}\label{fig:spotModel}
\end{centering}
\end{figure*}

@@

\section{Spot Distribution}
\newcommand{\maxSpots}{\#?}
We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.
We allow up to \maxSpots\ across the sphere of the brown dwarf, all with a constant temperature contrast.
We set the ``background'' at the measured effective temperature of 1614 K.

Figure \ref{fig:spotModel} shows the spot models fit to the light curve at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.
At all three wavelengths, the fitted brightness temperature contrast is around 50 K above the background.
These higher temperature spots are indicative of either holes in clouds or regions of elevated temperature.
The distribution of spots changes with wavelength, suggesting that the distribution of clouds or temperatures is complex.
The low amplitude and signal to noise of the light curves makes it difficult to put tight constraints on the spot distribution.
